External Patch Group Prior Guided Internal Subspace Learning for Real Image Denoising

### 2016-10-17 egpaper_for_review.tex
a

\subsection{Iterative Regularization}
Perfoming image denoising in one iteration is not enough for real noise since the noise is signal dependent. The removed noise in one iteration is largely dependent on the signal. Therefore, it is essential to add back some residuals removed in this iteration for the denoising of the next iteration.

@@

The PSNR and SSIM resluts are listed in Table \ref{tab1}. The number in red color and blue color means the best and second best results, respectively. From the Table \ref{tab1}, we can see that the external based method can already surpass largely the previous denoising methods. The improvement on PSNR over the second best method, i.e., TRD, is 0.44dB. The 
\begin{table*}\label{tab1}
\caption{Average PSNR(dB) results of different methods on 60 cropped real noisy images captured in \cite{crosschannel2016}.}
\label{tab1}
\begin{center}
\renewcommand\arraystretch{1}
\begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|c|}
\hline
 & \textbf{Noisy} &\textbf{CBM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}&\textbf{TRD}& \textbf{NI}& \textbf{NC} &\textbf{Guided}  &\textbf{Guided2} 
\\
\hline
PSNR & 34.51 & 34.58 & 34.52 & 36.19 & 37.40 & 37.75 & 36.53 & 37.57 &  \color{blue}{38.55} & \color{red}{ 38.80}
\\
\hline
SSIM & 0.8718  & 0.8748  & 0.8743   & 0.9470 & 0.9598 &  0.9617 & 0.9241  &  0.9514  & \color{blue}{0.9675} & \color{red}{0.9694}
\\
\hline
\end{tabular}
\end{center}
\end{table*}

>>>>

\subsection{Fast Patch Group Searching by Integral Image}
The searching of patch groups in images is inefficient if we search non-local similar patches to each local patch. To speed up the searching process and make our proposed method faster, we employ the technique of 'Summed Area Table' \cite{sat} for efficient PG searching. The SAT permits to evaluate the sum of pixel values in rectangular regions of the image with four operations, regardless of the region size. That is to say, we do not need do distance measure for each patch. It was first proposed under the name of summed area table\cite{viola2004robust}

@@

The PSNR and SSIM resluts are listed in Table \ref{tab1}. The number in red color and blue color means the best and second best results, respectively. From the Table \ref{tab1}, we can see that the external based method can already surpass largely the previous denoising methods. The improvement on PSNR over the second best method, i.e., TRD, is 0.44dB. The 
\begin{table*}\label{tab1}
\caption{Average PSNR(dB) results of different methods on 60 cropped real noisy images captured in \cite{crosschannel2016}.}
\label{tab1}
\begin{center}
\renewcommand\arraystretch{1}
\begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|c|}
\hline
 & \textbf{Noisy} &\textbf{CBM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}&\textbf{TRD}& \textbf{NI}& \textbf{NC} &\textbf{Guided}  &\textbf{Guided2} 
\\
\hline
PSNR & 34.51 & 34.58 & 34.52 & 36.19 & 37.40 & 37.75 & 36.53 & 37.57 &  \color{blue}{38.68} & \color{red}{ 38.89}
\\
\hline
SSIM & 0.8718  & 0.8748  & 0.8743   & 0.9470 & 0.9598 &  0.9617 & 0.9241  &  0.9514  & \color{blue}{0.9676} & \color{red}{0.9704}
\\
\hline
\end{tabular}
\end{center}
\end{table*}
